### 2015-10-09 manuscript.Rnw
write availability section

\texttt{rotl} is available both from the CRAN repository
(https://cran.r-project.org/package=rotl) and from GitHub
(https://github.com/ropensci/rotl).

>>>>

\texttt{rotl} is free, open source, and released under a Simplified
BSD license. Stable versions are available from the CRAN repository
\url{https://cran.r-project.org/package=rotl}, and development
versions are available from GitHub
\url{https://github.com/ropensci/rotl}.

Python \url{https://github.com/OpenTreeOfLife/pyopentree} and Ruby
\url{https://github.com/SpeciesFileGroup/bark} libraries to interact
with the OTL APIs are also available.
